Caribou Demographic Projection - interesting & informative title TBD

### 2022-12-12 analysis/paper/paper.Rmd
Adding prior calibration appendix.

---
title: "Caribou Demographic Projection - interesting & informative title TBD"
author:
  - name: Josie Hughes
    email: josie.hughes@ec.gc.ca
    institute: [ECCC]
    correspondence: true
  - name: Sarah Endicott
    email: sarah.endicott@ec.gc.ca
    institute: [ECCC]
    correspondence: false
  - name: Cheryl A Johnson
    email: cheryl-ann.johnson@ec.gc.ca
    institute: [ECCC]
    correspondence: false
institute:
  - ECCC: Environment and Climate Change Canada 
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      number_sections: no
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: CaribouDemographicModel.bib
csl: "../templates/journal-of-forest-ecology-and-management.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
editor_options: 
  chunk_output_type: inline
---

@@

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dpi = 300
)
```

@@

runScenarios =T 
```
TO DO: build large table of all parameters as the various sections are written. Adjust UI for consistent terminology along the way.

@@

```{r priors, echo=FALSE}

@@

  png(here::here("analysis/figures/Figure1_Example.png"),
    height = 4, width = fig_widths["mid"], units = "in",res=600)
  print(plotRes(scResults$rr.summary.all, "Female population size",obs=scResults$obs.all,
              lowBound=0,highBound=2000,facetVars=c("P","sQ")))
  dev.off()
}

@@

```{r fig1, fig.cap="Example figure.", cache=TRUE}
knitr::include_graphics(here::here("analysis/figures/Figure1_Example.png"))

@@

@@

```{r colophon, cache = FALSE}
# which R packages and versions?
if ("devtools" %in% installed.packages()) devtools::session_info()
```

@@

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```

>>>>

---
title: "Caribou Demographic Projection - interesting & informative title TBD"
author:
  - name: Josie Hughes
    email: josie.hughes@ec.gc.ca
    institute: [ECCC]
    correspondence: true
  - name: Sarah Endicott
    email: sarah.endicott@ec.gc.ca
    institute: [ECCC]
    correspondence: false
  - name: Cheryl A Johnson
    email: cheryl-ann.johnson@ec.gc.ca
    institute: [ECCC]
    correspondence: false
  - name: Anna Calvert
    email: anna.calvert@ec.gc.ca
    institute: [ECCC]
    correspondence: false
institute:
  - ECCC: Environment and Climate Change Canada 
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      number_sections: no
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: CaribouDemographicModel.bib
csl: "../templates/journal-of-forest-ecology-and-management.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
editor_options: 
  chunk_output_type: inline
---

@@

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figs/",
  dpi = 300
)
```

@@

runScenarios = T 
doPriorCalibration=T
```
TO DO: build large table of all parameters as the various sections are written. Adjust UI for consistent terminology along the way.

@@

```{r priors, echo=FALSE,message=FALSE}

@@

  png(here::here("figs/Figure1_Example.png"),
    height = 4, width = fig_widths["mid"], units = "in",res=600)
  print(plotRes(scResults$rr.summary.all, "Female population size",obs=scResults$obs.all,
              lowBound=0,highBound=2000,facetVars=c("P","sQ")))
  dev.off()
}

@@

```{r fig1, fig.cap="Example figure.", cache=TRUE}
#knitr::include_graphics(here::here("figs/Figure1_Example.png"))

@@

## Calibration of Priors

```{r priorCalibration, cache=TRUE,echo=FALSE, message=FALSE,results='hide'}
if(doPriorCalibration){

  #TO DO: move CaribouDemo_v1.15Reduce.R to paper directory. And produce pngs, rather than pdfs.
  source(here::here("analysis/scripts/calibratePriors.R"))
}else{
  KS<-read.csv(here::here("tabs/SurvKSAll.csv"))
}
  png(here::here("figs/PriorKSDists.png"),
    height = 4, width = fig_widths["two"], units = "in",res=600)
    base = ggplot(KS,aes(x=lse,y=KSDistance,color=sse))+
    geom_point()+facet_grid(scn~ssv,labeller="label_both",scales="free_y")+theme_bw()
    print(base)
  dev.off()

```{r PriorKSDists, fig.cap="Prior parameter values should be set so that, given minimal monitoring data ('All' scenario: 1 year of 1 collar per year), the posterior survival distribution is similar to the distribution of simulated outcomes from the national model, measured here by Komogorov-Smirnov distance [ks.test function in @R_R_2022]. Low values of the mean and standard deviations of the prior distribution of the random effect of year on slope (sse=0.034784, ssv=0.01, $\\sigma^2_S$ in Table @ref(tab:priors)) meet this condition (Fig @ref(fig:priorAllFits). Priors should also be vague enough so that, given intensive monitoring of populations where survival is higher or lower than the national average ('High' and 'Low' scenarios: 15 years of 300 collars per year from 97.5% and 2.5% quantiles of the national model), posterior survival distributions reflect local survival, rather than priors from the national model. When the multiplier on the prior standard deviation of the survival intercept (lse: $\\beta^S_0$ in Table @ref(tab:priors)) is < 5, the prior is not sufficiently vague to meet the latter condition." , cache=TRUE}
knitr::include_graphics(here::here("figs/PriorKSDists.png"))

#TO DO: figure out what to do about citations and references in figure captions. Or just fill them in manually at a later stage.

```{r PriorAllFits, fig.cap="Differences between posterior distributions from the Bayesian model and simulated outcomes from the national model, assuming minimal monitoring (1 years of 1 collar per year) of populations from the 50% quantile of the national model. The multiplier on the prior standard deviation of the survival intercept ($\\beta^S_0$ in Table @ref(tab:priors)) is set to 5 in these examples.", cache=TRUE}
knitr::include_graphics(here::here("figs/SurvsQStarts1ssv0.01.png"))

```{r PriorHighFits, fig.cap="Differences between posterior distributions from the Bayesian model and simulated outcomes from the national model, assuming intensive monitoring (15 years of 300 collars per year) of populations from the 97.5% quantile of the national model. The multiplier on the prior standard deviation of the survival intercept ($\\beta^S_0$ in Table @ref(tab:priors)) is set to 5 in these examples.", cache=TRUE}
knitr::include_graphics(here::here("figs/SurvsQStarts300highlse5.png"))

@@

```{r colophon, cache = FALSE}
# which R packages and versions?
#if ("devtools" %in% installed.packages()) devtools::session_info()
```

@@

```{r}
# what commit is this file at? 
#if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```
